A Container-Based Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-10-16 draft.tex
Revised sentences, closes #21

Besides being, all of them, population-based, they also share the common characteristic of
creating an initial set of random candidate solutions later used by a 
nature-inspired heuristic to generate a new set of candidates. 
Population-based algorithms are intrinsically parallel.
The fitness of each individual can be (in general) evaluated independently of 
others, and similarly, each population could evolve in isolation. Researchers use the term
multi-population based methods when referring to techniques using
many populations as part of their optimization strategy. 
Since earlier works, researchers have been proposing some form of parallelization
\cite{muhlenbein1988evolution} to increase these algorithms' scalability
by adding some form of interaction between populations running in isolation.
The island model was one of the first techniques proposed for parallelization,
which led to early proofs of speed-up \cite{gorges1990explicit,grosso1985computer}. 
% Repetitive - M
%The concept was to divide a large population into communicated subpopulations. 
Since then, other population-based algorithms have adopted the idea. 
Researchers have found additional benefits
besides the execution speed; these include avoiding a premature convergence and
maintaining the diversity of the global population \cite{li2015multi}.

@@

%% JJ Can you improve the redability of the paragraph below? 
%% Grammarly suggests that is hard to read, verly long sentences.
%% Edited a little - Mario
Cloud computing has become the standard way of running
enterprise applications.  Not only because of the convenience of the
pay-as-you-go model or the non-existent sunk cost of physical facilities, but also because
it offers a way of describing the infrastructure as part of the code, so that it
is much easier to reproduce results and this has been a boon for scientific
computing.  
However,  cloud computing has also been evolving, going from simply
putting old-style monolithic applications on virtual machines executing on an external 
data center to microservices \cite{microservices} and serverless architectures \cite{varghese2018next,Varghese2018849} 
that favor the parallel and asynchronous communication of
heterogeneous resources. In the process, a new methodology for designing 
{\em cloud-native applications} has been created, with brand new methods and
techniques \cite{Baldini2016287}. 
In these architectures, services, or even functions are seen as independent 
processing nodes, departing from the monolithic
and even distributed paradigms, and becoming a loosely coupled collection of {\em
stateless functions}\cite{malawski2017serverless}, that react to events. 
%and only come into existence while they are doing some processing.
Systems developed with the patterns outlined above have the
properties of a reactive system \cite{boner2014reactive}, and they are generally 
more flexible, fault-tolerant, and scalable. % Some properties and reference - Mario  
% Again, you have to justify the need for a reactive architecture and define it before this paragraph - JJ

>>>>

Besides being, all of them, population-based, they also share the
common characteristic of creating an initial set of random candidate
solutions which is later used by a nature-inspired metaheuristic to
generate a new set of candidates; there are parts of this process that
can be easily done in parallel. For instance, the fitness of each
individual can be (in general) evaluated independently of others, and
similarly, each population could evolve in isolation. Researchers use
the term multi-population based methods when referring to techniques
using many populations as part of their optimization strategy.  Since
earlier works, researchers have been proposing some form of
parallelization \cite{muhlenbein1988evolution} to increase these
algorithms' scalability by adding some form of interaction between
populations running in isolation.  The island model was one of the
first techniques proposed for parallelization, which led to early
proofs of speed-up \cite{gorges1990explicit,grosso1985computer}.
Since then, other population-based algorithms have adopted the idea.
Researchers have found additional benefits besides the execution
speed; these include avoiding a premature convergence and maintaining
the diversity of the global population \cite{li2015multi}.

@@

Cloud computing has become the standard way of running
enterprise applications.  Not only because of the convenience of the
pay-as-you-go model or the non-existent sunk cost of physical facilities, but also because
it offers a way of describing the infrastructure as part of the code, so that it
is much easier to reproduce results and this has been a boon for scientific
computing.
However,  cloud computing has also been evolving, going from simply
putting old-style monolithic applications on virtual machines executing on an external 
data center to microservices \cite{microservices} and serverless architectures \cite{varghese2018next,Varghese2018849} 
that favor the parallel and asynchronous communication of
heterogeneous resources. In the process, a new methodology for designing 
{\em cloud-native applications} has been created, with brand new methods and
techniques \cite{Baldini2016287}. 
In these architectures, services, or even functions are seen as independent 
processing nodes, departing from the monolithic
and even distributed paradigms, and becoming a loosely coupled collection of {\em
stateless functions}\cite{malawski2017serverless}, that react to events. 
%and only come into existence while they are doing some processing.
Systems developed with the patterns outlined above have the
properties of a reactive system \cite{boner2014reactive}, and they are generally 
more flexible, fault-tolerant, and scalable. % Some properties and reference - Mario  
% Again, you have to justify the need for a reactive architecture and define it before this paragraph - JJ
